---
title: "IODS course project"
author: "Laszlo Vincze"
output:
  html_document:
    theme: cosmo
    toc: true
    toc_depth: 2
    fig_caption: true
    fig_width: 6
    fig_height: 4
    code_folding: hide
---

***
  
```{r child = "chapter1.Rmd"}
```
  
***
  
```{r child = "chapter2.Rmd"}
```> cor.test(learning2014$Age, learning2014$Points)

	Pearson's product-moment correlation

data:  learning2014$Age and learning2014$Points
t = -1.1986, df = 164, p-value = 0.2324
alternative hypothesis: true correlation is not equal to 0
95 percent confidence interval:
 -0.24207559  0.05998263
sample estimates:
        cor 
-0.09319032 

> cor.test(learning2014$Attitude, learning2014$Points)

	Pearson's product-moment correlation

data:  learning2014$Attitude and learning2014$Points
t = 6.2135, df = 164, p-value = 4.119e-09
alternative hypothesis: true correlation is not equal to 0
95 percent confidence interval:
 0.3044463 0.5521335
sample estimates:
      cor 
0.4365245 

> t.test(learning2014$Points ~ learning2014$gender)

	Welch Two Sample t-test

data:  learning2014$Points by learning2014$gender
t = -1.1832, df = 107.84, p-value = 0.2393
alternative hypothesis: true difference in means is not equal to 0
95 percent confidence interval:
 -3.0896905  0.7799502
sample estimates:
mean in group F mean in group M 
       22.32727        23.48214 

> model <- lm(learning2014$Points ~ learning2014$Attitude + learning2014$gender + learning2014$Age)
> summary(model)

Call:
lm(formula = learning2014$Points ~ learning2014$Attitude + learning2014$gender + 
    learning2014$Age)

Residuals:
     Min       1Q   Median       3Q      Max 
-17.4590  -3.3221   0.2186   4.0247  10.4632 

Coefficients:
                      Estimate Std. Error t value Pr(>|t|)    
(Intercept)           13.42910    2.29043   5.863 2.48e-08 ***
learning2014$Attitude  0.36066    0.05932   6.080 8.34e-09 ***
learning2014$genderM  -0.33054    0.91934  -0.360    0.720    
learning2014$Age      -0.07586    0.05367  -1.414    0.159    
---
Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1

Residual standard error: 5.315 on 162 degrees of freedom
Multiple R-squared:  0.2018,	Adjusted R-squared:  0.187 
F-statistic: 13.65 on 3 and 162 DF,  p-value: 5.536e-08

***
